Quantum Semiprime Factorization: Leveraging Grover's Algorithm for Efficient Prime Decomposition

### 2025-03-02 LaTeX/paper.tex
Defined iteration count

  Grover's Algorithm is a quantum computing method 
  that can be used to search a database in $O(\sqrt{n})$ time 
  rather than the naive classical time complexity of $O(n)$\cite{grover}.

>>>>

  Grover's Algorithm is a quantum computing method 
  that can be used to search a database of $n$ values in $O(\sqrt{n})$ time 
  rather than the naive classical time complexity of $O(n)$\cite{grover}.

  The exact number of iterations required varies on a case-by-case basis,
  but is typically expressed as follows: in a search for one matching input
  state, $\frac{\pi}{4}\sqrt{N}$ iterations are required, and in a search
  for $k$ valid input states, $\sqrt{\pi}{4}\cdot \sqrt{\frac{N}{k}}$
  iterations are required, where $N$ is the size of the search domain.

  In most cases, $N=2^n$, where $n$ is the number of bits needed to represent
  the target value. This is by no means a steadfast rule, and is meant as 
  a helpful starting point for any confused readers attempting to implement
  something similar themselves.
